|

### 2021-11-23 08-Discussion.Rmd
Citations fixed!
End of day:

This chapter details the

@@

The aim of this thesis was to attempt to infer the causal effect of blood lipid levels on dementia outcomes.

In this chapter I will summarise the principal findings from my thesis, assess the unique contributions of this thesis to the field of research, discuss the implications for both clinical and public health policy, describe the overall strengths and limitations of this thesis as a whole, suggest avenues for impactful future research based on my findings and experiences.

In __Chapter \@ref(sys-rev-tools-heading)__ presents a new tool for the systematic searching of health-related preprints, and detail

In __Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)__ describe the methods and results of a comprehensive systematic review of the relationship between blood lipids (and treatments that modify them) and dementia outcomes.

In __Chapter \@ref(cprd-heading)__ presents an analysis of lipid-regulating use and dementia outcomes in the CPRD, a large scale

In __Chapter \@ref(ipd-heading)__ presents an individual patient data meta-analysis, using previously unanalysed data accessed via the Dementia Platform UK.

In __Chapter \@ref(tri-heading)__ presents a narrative summary of the evidence identified and produced by the preceding chapters, and proposes a new method of systematically integration of multiple evidence sources as part of quantitative triangulation exercise.

@@

## New evidence produced

Since the systematic review was performed, there have been some notable further analysis related to the central thesis question here. Two of these are discussed here notable studies are discussed here.

Found slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease [@iwagami2021]. Not inconsistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4.

@@

In relation to the suggestion in this analysis that raised triglycerides were associated with an increasede risk of vascular dementia, a 2021 study in a  125,727 Danish participants found the moderate hypertriglyceridemia was associated with increased risk of non-Alzheimer's dementia (`r estimate(1.79, 1.16,2.87,"HR")`).[@nordestgaard2021]

@@

As part

@@

Additionally, in hindsight, I may have considered a mor. However, under the conditions of my grant, the scope for chang

As a reflective process throughout the PhD, I maintained a catalogue of failures (available in Appendix \@ref(appendix-catalogue-failures)).

@@

The strengths a limitations of each component of this thesis are discussed in the respective chapters. Here I highlight the strengths and weakness of the thesis as a body of work.

This thesis has used multiple sources of evidence to examine the relationship between blood lipids levels and cholesterol risk.

@@

It has analysed two previously unanalysed datasets, adding useful information to the evidence base.

@@

__Strengths__
- New evidence sources for an under-studied condition
- Development of new methods and tool

__Weaknesses__
A general limitation of this thesis is the absence of known results/data. This occured in both the systematic review, via the selection of reporting results and potential for publication bias. It was also observeed.

These facts both potentially bias the summary associations observed here, in addition to weakening the precision of the estimates produced.

- Confounding by indication

- A lot of UK based data

There are several strengths and limitations to the work presented in this thesis. One particularly strength is the lengths gone to find all available published and unpublished evidence around the question, and to integrate this evidence in a coherent framework, taking into account the limitations of ach source and how these limitations may be used to provide

Need for large simple trials for common disease where small treatment effect can have large effect - [@yusuf1984]

This thesis is limited by the low response rate to data access requests, and the

The lack of large, precise studies made comparison across different types of evidence difficult, while the low number of eligible studies for a

@@

Across multiple sources of evidence, there was no consistent effect of blood lipids, or . Some

The clinical recommendations that can be drawn from the work in this thesis are limited, due to the low strength of evidence related to the

@@

Patients must live to a sufficient age to be at risk of dementia outcomes, which is substantially less like if high lipid levels in mid-life.

The role of lipid-lowering

As with many many studies of dementia outcomes, a key limiting factor of any analysis is the absence of a detailed pathological mechanism for Alzheimer's disease. It could well be that statins do have a true effect independently of lipid levels, though based on the certainty of evidence in NRSI, this is unlikely.

However, based on the available evidence

For other dementia outcomes,

@@

@@

<!-- TODO Could he get it work, could he feck. -->

@@

## Public involvement and engagement {#disc-PPI}

<!-- TODO May need to tone this down a little bit -->

Involving and engaging the public and patients has been a central theme to this thesis. 
Public engagement activities included

Public involvement also steered the creation of the topic

@@

Normalisation of inclusion of preprints in systematic reviews. Wider assessment of the evidence base that exists solely as preprinted literature ()

Studying of factors which influence eventual publication would also help to identify the extent and strength of publication bias by providing a

@@

@@

As discussed, there is an absence of evidence on vascular dementia across the evidence base, potentially driven (for NRSI) at the leasby a publication

@@

This is particularly relevant given that there was some evidence for an association of hypertriglyceraecia with vascular dementia. Future research should explicitly examine this relationship as part o f wider exploration of vascular disease.

 <!-- TODO See notes from Pat/Emma on this -->

@@

### Viewing of Mendelian randomisation studies

As noted in Chapter \@ref(sys-rev-heading-results), evidence synthesis theory and methods have not been sufficient developed for the inclusion of Mendelian randomisation studies.

A key issue arises from the lack of an established risk of bias tool, which adds uncertainty to the accuracy of risk-of-bias assessments which can influence future work based on them, as discussed in Chapter \@ref(7). In addition, a lack of guidance around whether the inclusion of two-sample Mendelian randomisation studies using identical summary statistics. This was illustrated in detail in Chapter \@ref(4), where XXX studies using the same , and meta-analysing these as independent effect estimates would provide an overly precise result. Finally, future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define it (e.g. genetic instrumental variable analysis).

@@

The field of quantitative triangulation is one ripe for future work. In the first instance, guidance

Finally, methods for the standardisation of meth

Use of the real-world evidence approach needs to be traded off against the important limitations that t

Talk about the problems with real world evidence, and highlight that even when using these techniques, you still don't get the correct answers.

Tie in with GDS comments on off-targets effect.

@@

@@

>>>>

TBC

@@

The aim of this thesis was to attempt to infer the causal effect of blood lipid levels on dementia outcomes. In this discussion, I will review the role of each chapter in the broader thesis, summarise the principal findings and contributions of this thesis, and discuss the implications of my findings for both clinical and public health policy. I consider the overall strengths and limitations of this thesis as a coherent body of work, and suggest avenues for impactful future research based on my findings and experiences.

## Chapter summary

This thesis is comprised of a mix of informative, methodological and applied chapters.

In Chapter __Chapter \@ref(sys-rev-tools-heading)__, I introduced the core concepts considered in thie

In __Chapter \@ref(sys-rev-tools-heading)__, I  presented a new tool for the systematic searching of health-related preprints, and detail

In __Chapters \@ref(sys-rev-methods-heading)__, I describe the methods of a comprehensive systematic review of the relationship between dementia outcomes and blood lipids (and treatments that modify them). The results of this analysis are then presented in __Chapter \@ref(sys-rev-results-heading)__.

In __Chapter \@ref(cprd-heading)__, I describe an analysis of lipid-regulating use and dementia outcomes in the CPRD, a large scale electronic health database. I make use of control outcomes to illustrate insufficiently controlled biases

In __Chapter \@ref(ipd-heading)__, I present an individual patient data meta-analysis, using previously unanalysed data accessed via the Dementia Platform UK to add to the evidence base on the association of blood lipids and dementia outcomes.

Finally, in __Chapter \@ref(tri-heading)__ I propose a new method of systematically integration of multiple evidence sources as part of quantitative triangulation exercise. I illustrate the method by considering two causal questions (LDL-c and Alzheimer's disease; triglycerides and vascular dementia), drawing on the evidence identified or produced by previous chapters.

@@

## Summary of principle findings

Overall, I did not identify a consistent effect of any blood lipid fraction (total cholesterol, LDL cholesterol, HDL cholesterol or triglycerides) on any dementia outcome (all-cause dementia, Alzheimer's disease or vascular dementia).

While published non-randomised studies provided evidence for a protective effect of statin use on Alzheimer's disease, this effect was not maintained when incorporated along with other sources of evidence in a quantitative triangulation framework. However, this equally may indicate that statins have a pleiotropic effects on Alzheimer's disease, that is an effect other than through lipid-lowering. However, this observed effect could also be due to reporting biases, a

The inclusion of preprints

Statins were by far the most studied lipid-regulating agent in relation to dementia outcomes, a unsurprising finding given the large proportion of patients taking statins as indicated by my analysis of the CPRD data.

The inclusion

## New evidence

Since the systematic review described in this thesis was performed, there have been two notable analysis of large cohorts performed related to the central thesis question here. Two of these are discussed here notable studies are discussed here.

The first a large scale analysis of blood lipids in the CPRD, which found a slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease.[@iwagami2021] These findings are n Not inconsistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4.

@@

An analysis of 502,226 participants of the UK BioBank found no association between lipids at mid-life and dementia outcomes (women: TC `r estimate(1.04,.99,1.09,"HR")`, HDL `r estimate(0.95,.83,1.1,"HR")`, LDL `r estimate(1.6,1,1.13,"HR")`/men: TC `r estimate(0.98,.93,1.03,"HR")`, HDL `r estimate(1.1,.95,1.29,"HR")`, LDL `r estimate(.97.91,1.04,"HR")`).[@gong2021] Results were boardly similar between the all-cause dementia, Alzheimer's disease and vascular dementia outcomes. This is comparable to my findings.

## Summary of contributions

The research described in this thesis represents a number of novel contributions to the the fields of evidence synthesis

With respect to dementia epidemiology, the systematic review reported in Chapters

@@

As a reflective process throughout the PhD, I maintained a catalogue of failures available in Appendix \@ref(appendix-catalogue-failures), describing . here I present a more general rel

@@

Additionally, in hindsight, I may have considered a more methodological thesis. The Chapter's I enjoyed working on the most (Chapters \@ref())

Further, a more aggressive approach to , Potential approaches could have included sending emails via my supervisors

However, normal opportunities to tie people down in person were suspended during COVID.

@@

The strengths a limitations of each component of this thesis have been discussed in the respective chapters. Here I highlight the strengths and weakness of the thesis as a body of work.

#### Strengths

This thesis has used multiple sources of evidence to examine the relationship between blood lipids levels and cholesterol risk in a systemtatic manner, including diverse sources of evidence, inclu

@@

It has provided new evidence on an understudied condition (vascular demenita), analysing three previously unexplored datasets to provide evinde

- New evidence sources for an under-studied condition
- Development of new methods and tool

One particularly strength is the lengths gone to find all available published and unpublished evidence around the question, and to integrate this evidence in a coherent framework, taking into account the limitations of ach source and how these limitations may be used to provide

#### Weaknessess

@@

A general limitation of this thesis is the absence of known results/data. This occurred in both the systematic review, via the selection of reporting results and potential for publication bias. It was also observed.

Similarly, missing evidence was a common theme across this thesis. In Chapters \@ref(hold)/\@ref(hold), several studies stated that they did not report the results of an analysis because the results were not significant. This was particularly common among non-randomised studies of exposure examining blood lipids directly. Fortunately, new tools such as the forthcoming ROB-ME.

Similarly, an absence of evidence on vascular dementia limits the certainty. In both these cases, accounting for missing evidence will be an important part of future evidence snythesis work on this topic.

Missing evidence in the form of a poor response to data access requests was also observed in the IPD analysis reported in Chapter \@ref(hold).

A final weakness of this thesis is the geographical focus. All primary analysis presented drew on data from the UK population (CPRD, CaPS, EPIC Norfolk, Whitehall II).

@@

The clinical recommendations that can be drawn from the work in this thesis are limited, due to the low strength of evidence. Across multiple sources of evidence, there was no consistent effect of blood lipids on dementia outcomes.

However, even under the scenario that a strong protective effect was identified, whether or not to prescribed a statin at mid-life will always be guided by factors other than dementia prevention. Patients must live to a certain age in order to be at risk of dementia (with the exception of familial early onset dementias), which is substantially less likely if hypercholesterolemia is left unchecked.

However, while this thesis did not provide any evidence for a protective effect of lipid-lowering, it similarly did not provide any evidence for a harmful effect of statin exposure on dementia outcomes.

@@

As with many many studies of dementia outcomes, a key limiting factor of any analysis is the absence of a detailed pathological mechanism for the condition. It could well be that statins do have a true effect independently of lipid levels, though based on the certainty of evidence in NRSI, this is unlikely.

@@

The absence of an effect of blood lipids on dementia outcomes is an unh

However, future work

@@

@@

@@

Given the evidence that this thesis produced on the usefulness of including preprints, normalisation of inclusion of preprints in systematic reviews. Wider assessment of the evidence base that exists solely as preprinted literature ()

Meta-epidemiological studies examining the factors which influence eventual publication would also help to quantify the extent and strength of publication bias

@@

Future work should also address how to handle discrepancies between the preprinted and published versions of a paper, particularly if the results are subtantially different between the two versions.

@@

As discussed in an earlier section, there is an absence of evidence on vascular dementia across the evidence base

Future work should aim to address this evidence gap.

@@

This is particularly relevant given that there was some evidence for an association of hypertriglyceraemia with vascular dementia. Future research should explicitly examine this relationship as part of wider exploration of vascular disease.

@@

### Reviewing Mendelian randomisation studies

As noted in previous chapters, evidence synthesis theory and methods have not been sufficient developed for the inclusion of Mendelian randomisation studies.

A key issue arises from the lack of an established risk of bias tool, limiting future work that requires systematic risk-of-bias assessment, such as the triangulation framework presented in Chapter \@ref(hold). In addition, a lack of guidance around whether the inclusion of two-sample Mendelian randomisation studies using identical summary statistics. This was illustrated in detail in Chapter \@ref(4), where XXX studies using the same , and meta-analysing these as independent effect estimates would provide an overly precise result. Finally, future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define it (e.g. genetic instrumental variable analysis).

@@

It is customary at this point to recommend that a large scale. However, based on the evidence described. In addition, logistical challenges in relation

In summary, there is a need to make better use of the existing evidence accounting for the

The field of quantitative triangulation is one ripe for future work.

In the first instance, guidance

Finally, accounting for bias (and indirectness, if considering causal effects rather than a summary of the literature) is essentially in the interpretation of published literature. While this can take many forms, from the stratification of forest plots by overall risk of bias level, to the or to the more advance bias adjustment approach detailed here, it is insufficient to draw clinical recommendations from meta-analysis that treat effect estimates as if they were unbiased.

@@

The

In addition, I have created

and proposed a novel combination of existing methods in pursuit of a generalised quantitative framework.

@@

Blood lipids

### 2021-11-23 front-and-back-matter/99-appendices.Rmd
End of day:

```{r, echo = FALSE, warning=FALSE, message=FALSE}

knitr::read_chunk(here::here("R/appendix.R"))
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

<!-- TODO Need to include -->

### Forest plots for lipid fractions {#lipid-fraction-forest-plots}

<!-- TODO Need to add labels/captions to these -->

<!----------------------------------------------------------------------------->
```{r obsLipidsDementiaTC, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_TC_.png"))
```
<!----------------------------------------------------------------------------->

<!----------------------------------------------------------------------------->
```{r obsLipidsDementiaLDL, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_LDL_.png"))
```
<!----------------------------------------------------------------------------->

<!----------------------------------------------------------------------------->
```{r obsLipidsDementiaHDL, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_HDL_.png"))
```
<!----------------------------------------------------------------------------->

<!----------------------------------------------------------------------------->
```{r obsLipidsDementiaTG, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_TG_.png"))
```
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}
<!----------------------------------------------------------------------------->
### Amendments to protocol {#appendix-cprd-amendments}

@@

failing to realise that the initial codelist used for the positive control outcome of IHD in the CPRD analysis (Chapter \@ref(cprd-heading))

@@

### Introduction

Risk of bias assessment - evaluation of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@cochranechpt7] A well-developed family of tools is widely used, which have in common the characteristic that they evaluate specific domains of bias rather being constructed as a checklist or a quantitative score.[@cochranechpt7] These tools include the RoB 2 tool for randomized trials,[@sterne2019rob] the ROBINS-I tool for non-randomized studies of interventions,[@sterne2016robins] the QUADAS 2 tool for test accuracy and the ROBIS tool for systematic reviews.[@whiting2011quadas] Within each bias domains a judgement is reached about the strength of the study in that regard: for example, the first domain in the Cochrane RoB 2 tool deals with bias arising from the randomization process.[@sterne2019rob] Accessible graphics summarizing the results of these domain-based risk-of-bias assessments are included in reports of systematic reviews. A convenient plot in many reviews is a "traffic light" plot, which tabulates the judgement for each study in each domain. For larger numbers of studies, when such a table become unmanageable, a popular alternative is a weighted bar plot, which show the proportion of information with each judgement for each domain.[@higgins2008assessing]

Researchers can face a number of barriers in creating these plots. While some evidence synthesis platforms, such as Cochrane's Review Manager,[@cochrane2014review] are able to produce these visualizations, not all researchers use these systems to conduct their systematic reviews, and copying the risk-of-bias data into these systems simply to produce the plots is inefficient and error prone. Likewise, creating the figures by hand, through software such as MS PowerPoint or Adobe Illustrator, may lead to unintentional errors and require the plots to be redrawn during an update to the review. Additionally, while the field of evidence synthesis software has grown rapidly in recent years,[@marshall2015systematic] this growth has not been equally distributed across the different aspects of the systematic review process. For example, a recent review found several software offerings aimed specifically at the abstract screening stage of the review process,[@harrison2020software] but no similar time- and error-reducing tool has been proposed for visualizing the results of risk-of-bias assessments.

Fortunately, tools such as R, RStudio and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce such a tool.[@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias VISualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily. Originally created for use with the major risk-of-bias assessment tools used in health research, the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.

The tool is open-source and available to use free of charge. Users can download a stable version of the R package from CRAN (<https://cran.r-project.org/package=robvis>); or access and contribute to the development version via GitHub (<https://github.com/mcguinlu/robvis>).

### Development

Development of `robvis` began in April 2019 at the Evidence Synthesis Hackathon (ESH), an event which brings together interested researchers, practitioners and coders to discuss and develop new open-source evidence synthesis technologies. Test versions of both the R package and the web app were made available in early June 2019, with attendees of the ESH and members of the Bristol Appraisal and Review of Research (BARR) group at the University of Bristol being invited to test the tool and provide feedback. This feedback, along with other feature suggestions from the wider evidence synthesis community captured via GitHub issues, was incorporated and the first release version of the package was uploaded to CRAN in November 2019. The tool has been well received and is beginning to be cited in the evidence synthesis literature.[@gibb2019consistent; @habadi2019prevalence; @veloso2020effectiveness; @simillis2020; @tanneru2020]

### Installation

A stable version of `robvis` is hosted on the Comprehensive R Archive Network (CRAN) and can be installed using:

```{r, eval = FALSE}
install.packages("robvis")
```

As development of `robvis` is ongoing, new features are often available in the development version some time before they appear in the stable CRAN version. The most recent development version can be install from GitHub using:

```{r, eval = FALSE}
devtools::install_github("mcguinlu/robvis")
```

### Usage

`robvis` contains two main functions. The first, `rob_traffic_light()`, creates a traffic light plot by tabulating each study by each domain, providing a more detailed view of the results of the risk-of-bias assessment. The second, `rob_summary()`, creates a weighted bar plot showing the proportion of information with each judgement for each domain in the assessment tool specified.

A worked example using these functions is outlined below, showing the ease with which risk-of-bias plots can be created using `robvis`. A detailed description of the additional options that can be used with each function is presented in Table \@ref(tab:robvisarguments)

Using the example data set (`data_rob2`) which is built into the package and is presented in Table \@ref(tab:robdata) for reference, the traffic light plot shown in Figure \@ref(fig:trafficplot) is created using:

<!-- TODO __NEED TO ADD DATA HERE!__ -->

rob_traffic_light(data = data_rob2,
                  tool = "ROB2",
                  psize = 15)
```

```{r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`", out.width = "100%", fig.align = "centre"}

plotdata <- robvis::data_rob2

tfplot <- robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 5)

robvis::rob_save(tfplot, 
                 file = "figures/sys-rev-tools/example-rob-traffic-light-plot.png")

knitr::include_graphics("figures/sys-rev-tools/example-rob-traffic-light-plot.png", auto_pdf = TRUE)
```

Similary, using the same data set, the summary barplot shown in Figure \@ref(fig:summaryplot) is created using:

rob_summary(data = data_rob2,
            tool = "ROB2", 
            overall = TRUE)

```{r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis` and the example ROB2 dataset", out.width = "100%"}

sumplot <- robvis::rob_summary(plotdata, "ROB2", overall = TRUE)

robvis::rob_save(sumplot,
                 file = "figures/sys-rev-tools/example-rob-summary-barplot.png")

knitr::include_graphics("figures/sys-rev-tools/example-rob-summary-barplot.png")

A list of arguments available to the two functions in robvis are shown in Table \@ref(tab:robvisarguments)

```{r robvisarguments, echo = FALSE, eval = TRUE}

arguments <- data.frame(stringsAsFactors=FALSE,
              argument = c("data", "tool", "colour", "overall", "weighted",
                           "psize"),
     rob_traffic_light = c("\nX", "X", "X", "", "", "X"),
           rob_summary = c("X", "X", "X", "X", "X", ""),
           Description = c(
"Defines the dataframe containing the summary (domain) level risk-of-bias assessments. See the text and Table 1 for the format expected by `robvis`",
"Defines the risk of bias assessment tool used. The RoB2 (`tool=\"ROB2\"`), ROBINS-I (`tool=\"ROBINS-I\"`), and QUADAS-2 (`tool=\"QUADAS-2\"`) assessments tools are currently supported. Other tools can be visualised using the generic template (`tool = \"Generic\"`)",
"Defines the colour scheme for the plot. The default is `colour = \"cochrane\"` which uses the \"Cochrane\" (red, yellow, green) colours, while a preset option for a colour-blind friendly palette is also available (`colour = \"colourblind\"`). Alternatively, users can specify their own colour scheme e.g. `colour = c(\"#f442c8\", \"#bef441\", \"#000000\")`",
"Defines whether to include an additional bar showing the distibution of overall risk of bias judgements in the summary barplot figure. Default is `overall = FALSE`.",
"Defines whether weights should be used to produce the summary barplot figure. Default is `weighted = TRUE`, in line with current Cochrane Collaboration guidance.",
"Defines the size of the points in the traffic light plot. Default is `psize = 20`."))

if(doc_type == "docx"){

  knitr::kable(arguments,
               escape = T,
             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",

             col.names = c("Argument","rob_traffic_light()","rob_summary()", "Description"))

} else {

  knitr::kable(
    arguments,
    format = "latex",
    booktabs = TRUE,
    longtable = TRUE,
    caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
    align = c("l", "c", "c", "l"),
    col.names = c(
      "Argument",
      "rob_traffic_light()",
      "rob_summary()",
      "Description"
    )
  ) %>%
    column_spec(4, "5cm") %>%
    kable_styling(
      font_size = 9,
      bootstrap_options = c("striped", "hover"),
      latex_options = c("repeat_header", "striped")
    )
}

### Reception and Future Plans

```{r, echo = FALSE}
robvisstats <- cranlogs::cran_downloads("robvis", from = "2019-11-22", to = "2021-12-01")

robvis_downloads <- format(plyr::round_any(sum(robvisstats$count),100, f = floor), scientific = FALSE)

date <- format(as.Date("2021-12-01"),"%B %Y")

As of `r date`, `robvis` has been downloaded more than `r robvis_downloads` times. It has been well received but the systematic review community, and has been cited frequently in the published literature. A paper describing the tool was published in a special issue of Research Synthesis Methods focusing on data visualisation methods. A chapter on the tool has been incorporated in to the "Doing Meta-Analysis in R" online textbook.[@mathias_harrer_2019_2551803]

While `robvis` is a stable package, a range of additional functionality could be added. At present, the number of tools with a specific template included in `robvis` is limited - adding additional templates is a priority. For example, a template for ROBIS, a tool for assessing risk of bias in systematic reviews, is in developement.[@whiting2016robis] Additionally, the tool does not yet allow for the production of paired forest plots, where the risk-of-bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initially considered to be beyond the scope of the tool, as it involves the visualization of something other than risk-of-bias assessments. However, following user-driven demand, this functionality is in development and will be available in the near future. Finally, we would like to add similar functionality to that provided by the `metafor::reporter()` function, which generates a brief paragraph of text describing the results of a meta-analysis. The future `robvis::reporter()` function would provide a boilerplate description of the assessment tool used and the key domains at risk of bias.

## Creating

@@

\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf}

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source(here::here("R/helper.R"))
knitr::read_chunk(here::here("R/appendix.R"))
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

@@

<!----------------------------------------------------------------------------->
## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}
<!----------------------------------------------------------------------------->

### Amendments to protocol {#appendix-cprd-amendments}

<!----------------------------------------------------------------------------->
## Chapter \@ref(tri-heading) {#appendix-tri-analysis}
<!----------------------------------------------------------------------------->
### Calculation of average adjustment from expert elicitation

@@

Failing to properly scope the literature and correctly estimate the number of studies returned by the search

failing to realise that the initial code list used for the positive control outcome of IHD in the CPRD analysis (Chapter \@ref(cprd-heading))

<!-- TODO Include the early analysis we did here, that did not work as a result of limited scope. Could include some of the genetic work also. Will additionally need to put the relevant materials from the paper in the  -->

@@

@@

\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf}

### 2021-11-23 front-and-back-matter/_acknowledgements.Rmd
End of day:

There are so many people without whom this would not have been possible:

[**Check all name spellings**]

Sharen O'Keffe
Neal Haddaway
Martin Westgate

robvis contributors: (there are at least 3)

@@

Those who contributed their time to dual marking papers and code with me,

Thanks to Francesca for sharing advance copy of review of Mendelian randomisation studies, to inform choice of tool.

I am a NIHR Doctoral Research Fellow with grant code **TBC**. The funding source had no role in the design, conduct of the study, collection, management, analysis and interpretation or preparation, review, or approval of the thesis.

@@

@@

Finally, thanks to parents and Ciara Gardiner.

>>>>

There are so many people without those input this work would have been severly diminised:

__Supervisors__

Sharen O'Keffe, Neal Haddaway, Martin Westgate, Emily Hennessy, Randall Boyes, Alex J Fowler,

`robvis` contributors: (there are at least 3)

@@

Those who contributed their time to dual marking papers and data extracting with me,

Thanks to those researchers, namely Francesca for sharing advance copy of her review of tools to assess Mendelian randomisation studies, and Rebecca Turner for pointing me towards the code underpinning the quantitative triangulation framework.

I am a NIHR Doctoral Research Fellow, supported by grant **TBC**. The funding source had no role in the design, conduct of the study, collection, management, analysis and interpretation or preparation, review, or approval of the thesis.

@@

My student, Georgia Gourlay

@@

Thanks to the Canygne hall crew, for keeping me sane during write-up.

Finally, thanks to parents and

Finally, thanks to my fianceé and project-manager-extordinaire, Ciara Gardiner.
